Unify Language and Vision: An Efficient COVID-19 Tomography Image Classification Approach

### 2020-11-06 A-BasicCommom/CVPR2021/cvpr_covid.tex
1.cov

%%%%%%%%% TITLE
\title{Enhance Image Classification Performance Via Unsupervised Pre-trained Transformers Language Models}

@@

  Image classification and categorization are essential to the capability of telling the difference between images for a machine.
  As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
  and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.

@@

  Unsupervised pre-training is important to modern research of deep learning.
  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches
  in Computer Vision tasks in 2009, and later from 2010 to 2016,
  Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks,
  thus, can be omitted in some cases.
  However, it started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
  Not long before Devin \etal~\cite{devlin2019bert}'s BERT language model dominates in most frequently used tasks in natural language processing,
  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
  The pre-training process becomes one of the most important procedures in deep learning.

@@

%-------------------------------------------------------------------------
\subsection{Approach}

My approach consists of a pre-training state followed by a fine-tuning stage.
In pre-training, I use BERT objectives and the sequence Transformer architecture to predict language tokens.

@@

\par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial datasets, which has 2 and 4 classes.
The \textit{Case-2} dataset annotated civil and criminal cases, and the \textit{Case-4} dataset annotated by civil, criminal, intellectual property, and administrative cases.
The \textit{Case-2} dataset has $19508$ training documents and $2000$ test documents, and the \textit{Case-4} dataset has $34789$ training documents and $2013$ test documents.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|r|}
\hline
Language Model 	& Dataset & Accuracy \\
\hline\hline
RoBERTa-wwm-ext-large & Case-2	&	99.80\% \\
RoBERTa-wwm-ext-large & Case-4	&	99.76\% \\
RBTL3  & Case-4	&	96.35\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on different datasets in the document classification task.}
\end{table}
%-------------------------------------------------------------------------

@@

I design simple classification models without too many layers, as Figure (1) shows.
And use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
The model architecture has seven functional layers:

@@

\par The CIFAR-10 dataset contains 60000 color images with a resolution of 32x32 in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
then encode other meta-data if provided, as a sequence of ASCII characters.
In the Concatenation layer, the pixel-channel value and metadata are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
and put a $\textbf{[SEP]}$ token between channel values and metadata, put a special token of $\textbf{[SEP]}$ at the end.
In the Trim layer, due to the limit on the max sequence of the BERT language model, a sequence larger than $512$ needs to be trimmed before sending it to the BERT model.
Keep the first 256 characters and last 256 characters of the concatenated sequence, trimmed result contains the first 255 red-channel value,
some blue-channel value, and all the meta value in common cases.
In the Encoder layer and the Embedding layer, trimmed sequence of values are encoded by BERT-like models,
and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as equation (2), is used.
In the Output layer, the classification label of the image is feed in the model.

@@

\par It is intuitive for the model to use both the channel values and the metadata during the training phase.
For the CIFAR-10 and CIFAR-100 dataset, the metadata is the filename of the images, which can be treated as the supervised description of the image.
Peek some the filenames, \eg \textit{wagon\_s\_001343.png}, \textit{banana\_boat\_s\_001615.png}, and \textit{delivery\_truck\_s\_001529.png},
and it is beneficial for the classification model to understand the supervised descriptive information for the image.

@@

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{roberta-cifar.pdf}}
\end{center}
   \caption{Accuracy of the image classification models with the pre-trained language encoder on the CIFAR-10 and CIFAR-100 dataset in the training epochs.}
\label{fig:short}
\end{figure*}

@@

\par When fine-tuning, as Figure (2), I check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|r|}
\hline
Language Model 	& Dataset & Epoch & Accuracy \\
\hline\hline
RBT3   & CIFAR-10 & 6	&	99.74\% \\
RBTL3  & CIFAR-10 & 6	&	99.72\% \\
RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
\hline
RBT3   & CIFAR-100 & 12	&	99.66\% \\
RBTL3  & CIFAR-100 & 6  & 	99.10\% \\
RoBERTa-large & CIFAR-100 & 16 &	99.76\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
RoBERTa-large is short for RoBERTa-wwm-ext-large.}
\end{table}

@@

 This paper proposed a novel idea by using pre-trained language models for image representation and take image classification as an example of its performance in Computer Vision tasks.
 The finding might benefit various subjects, namely Education, Medical, Chemistry, Physics, Cosmology, Geography, Climate and Materials Science for their specific research.
Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
the model achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.

>>>>

%%%%%%%%% TITLE
\title{Unify Language and Vision: An Efficient COVID-19 Tomography Image Classification Approach}

@@

  An accurate and efficient image classification algorithm used in the COVID-19 detection for lung tomography can be of great help for doctors working in places without advance equipments.
  The machine with high accuracy COVID-19 classification model can relief the burden by making testing and checking thousands of people's tomography images easy for a specific region which suffers from the COVID-19 outbreak incidents.
  By encoding image pixels and metadata using the pre-trained language models of \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers,
  then connect to a fully connected layer,
  the classification model outperforms the ResNet model and the DenseNet image classification model,
  and achieved accuracy of $99.51\%\sim100.00\%$ on the COVID-19 tomography image test set.

@@

  Natural language processing and Computer Vision are two domains of the Computer Science.
  However, the encoded representation for the languages and images showed that there are potential connections between what we see and what we write.
  Unsupervised pre-training is important to modern research of deep learning.
  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches
  in Computer Vision tasks in 2009, and later from 2010 to 2016,
  Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks,
  thus, can be omitted in some cases.
  However, it started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
  Not long before Devin \etal~\cite{devlin2019bert}'s BERT language model dominates in most frequently used tasks in natural language processing,
  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
  The pre-training process becomes one of the most important procedures in deep learning.

@@

%-------------------------------------------------------------------------
\subsection{Dataset}

In total, 349 computed tomography images were collected from the COVID-19 reports in the MedPix, LUNA, Radiopaedia, PubMed Central databases, which sizes range from $1637\times1225$ to $148\times61$.

\subsection{Approach}

My approach consists of a pre-training stage followed by a fine-tuning stage.
In pre-training, I use the BERT objectives and the sequence Transformer architecture to predict language tokens.

@@

@@

@@

I design simple classification models without too many layers, as Figure (1) shows.
And use the COVID-19 lung tomography dataset as an example to show the architecture of the model.
The model architecture has seven functional layers:

@@

\par The original tomography images are of different sizes and often too large to feed into the model.

The COVID-19 lung tomography dataset contains 251 covid images and 291 covid negative images in the training set,
and contains 98 covid image and 100 covid negative images in the test set.
All images are resized to a resolution of 32x32 pixels, RGB channels are kept and the alpha channel is discarded.
Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
then encode other metadata which is the file name of each image, as a sequence of ASCII characters.
In the Concatenation layer, the pixel-channel value and metadata are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
and put a $\textbf{[SEP]}$ token between channel values and metadata, put a special token of $\textbf{[SEP]}$ at the end.
In the Trim layer, due to the limit on the max sequence of the BERT language model, a sequence larger than $512$ needs to be trimmed before sending it to the BERT model.
Keep the first 256 characters and last 256 characters of the concatenated sequence, trimmed result contains the first 255 red-channel value,
some blue-channel value, and all the meta value in common cases.
In the Encoder layer and the Embedding layer, trimmed sequence of values are encoded by BERT-like models,
and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as equation (2), is used.
In the Output layer, the classification label of the image is feed in the model.

@@

\par It is intuitive for the model to use both the channel values and the metadata during the training phase.
For the COVID-19 lung tomography dataset, the metadata is the filename of the images, which can be treated as the supervised description of the image.
Peek some the filenames, \eg \textit{covid\_201\_1.png}, \textit{covid\_201\_2.png}, and \textit{noncovid\_001\_1.png},
and it is beneficial for the classification model to understand the supervised descriptive information for the image.

@@

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{image-classification.pdf}}
\end{center}
   \caption{Accuracy of the image classification models with the pre-trained language encoder on the CIFAR-10 and CIFAR-100 dataset in the training epochs.}
\label{fig:short}
\end{figure*}

@@

\par When fine-tuning, as Figure (1), I check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|r|}
\hline
LM& Dimensions & Epochs & Accuracy \\
\hline\hline
RBT3   & 768 & 8	&	99.51\% \\
RBTL3  & 1024 & 3	&	100.00\% \\
RoBERTa-large  & 1024  & 10	&	100.00\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language image classification models on the COVID-19 dataset.
RoBERTa-large is short for RoBERTa-wwm-ext-large. LM is short for Language Model}
\end{table}

@@

This paper proposed a novel idea by using pre-trained language models for image representation and take image classification as an example of its performance in Computer Vision tasks.
The finding might benefit the diagnostics of the COVID-19, and improve the accuracy by combining language pre-trained model and the metadata of the computed tomography.
Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
the model achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.
Tested on the COVID-19 tomography image test set, the proposed model achieved accuracy of $99.51\%\sim100.00\%$.
